\subsection*{Participation}
Attendance will be taken during the class. Students who are unable to attend should contact the instructor before class if at all possible. Failure to contact the instructor before or after the class will result in a participation grade of \textbf{0}. Students who cannot attend class and notify the instructor may have some points deducted from the week's participation score, but it will not be a \textbf{0}. If a student provides sufficient evidence (doctor's note, police report, or similar) for a valid excuse (illness, accident, deployment), no points shall be deducted for the absence. The standard requirement for coursework is that students should expect to spend 3 hours in weekly work for every 1 hour of credit. This includes preparation, activities, and evaluation.

\subsection*{Quizzes}
Quizzes shall be taken closed book at the end of class. They will have a time limit of 90 minutes. Students who are absent during a quiz will have to contact the instructor \emph{as soon as possible} to reschedule it. \emph{This is the student's responsibility not the instructor's}. Failure to reschedule the quiz prior to the following week's class will result in a grade of \textbf{0} and no make-up will be allowed.

\subsection*{Assignments}
Assignments are due by the end of the class day. Students are encouraged to submit their assignments ahead of time. Hard copies can be submitted during class, but they must be given \emph{to the instructor}. Digital copies can be emailed to the instructor, but they must be sent as either Adobe PDF (\textbf{preferred}) or Microsoft Word files. Assignments submitted late will be penalized two (2) points per working day for the first week, then ten (10) points per week thereafter. All assignments must follow these requirements:
\begin{itemize*}
	\item Be typed, double-spaced, using Times New Roman font (size 12), with 1 inch margins on all sides.
	\item Citations and references must follow APA Style format.
	\item Include a cover page containing the tile of the assignment, the student's name, the professor's name, the course title, and the date.
	\item The cover page and the reference page are \emph{not included} in the required assignment page length.
	\item You may use popular sites such as Google and Wikipedia to get information, but you are not allowed to reference it in your paper. Websites are good for \emph{finding} sources but are not good sources alone.
\end{itemize*}
