\pagebreak
\section*{Assignment 1: Essay}
\emph{Due Week 4 and worth 100 points}

Choose one of the three reading selections from the list of topic choices below. Read the selection in the textbook. Write a three to four (3-4) paragraph essay (250 words) which analyzes the ``surprise ending'' of the reading selection.

\subsection*{Topic Choices}
\begin{enumerate*}
	\item Reading selection from Descartes' \emph{Discourse on the Method} (Part IV). Descartes begins with the problem of being able to prove his own existence but ends up with an argument proving the existence of God. Read more about the \emph{Discourse on the Method} located at http://www.earlymoderntexts.com/pdf/descdisc.pdf. 

	\item Reading selection from Swift's ``A Modest Proposal.'' Swift begins with offering the solution that the English could do things which might solve the problem of over-population and the mistreatment of citizens in Ireland and ends by offering the solution that an internal change in the Irish government would best solve the problem of over-population and a populace victimized by its own government. Read more about ``A Modest Proposal'' located at http://www.victorianweb.org/previctorian/swift/modest.html.

	\item Two reading selections from Voltaire's \emph{Candide}. The story begins by acknowledging the foolishness of the superstitious traditions held by the people in the city of Lisbon but ends by confirming Voltaire's belief that religion in general is equally based in false superstitions.
\end{enumerate*}

The specific course learning outcomes associated with this assignment are:
\begin{itemize*}
	\item Explain how key social, cultural, and artistic developments contribute to historical changes.
	\item Explain the importance of situating a society's cultural and artistic expressions within a historical context.
	\item Examine the influences of intellectual, religious, political, and socio-economic forces on social, cultural, and artistic expressions.
	\item Identify major historical developments in world cultures from the Renaissance to the contemporary period.
	\item Use technology and information resources to research issues in the study of world cultures.
	\item Write clearly and concisely about world cultures using proper writing mechanics.
\end{itemize*}

\rubricQuarter{
	Clearly state the surprise ending and identify the point when realization occurred that the ending would be different.
	& Did neither; omitted information and/or included irrelevant information.
	& Partially completed at least one; omitted some key information.
	& Sufficiently completed both.
	& Fully completed both. \\ \hline

	Evaluate the author's success at providing a believable ``surprise ending.''
	& Did not evaluate; omitted information and/or included irrelevant information.
	& Partially evaluated; omitted some key information.
	& Sufficiently evaluated.
	& Fully evaluated.
}
