\documentclass{article}
\usepackage{syllabus}

\title{HUM 112: World Cultures 2}
\date{Autumn 2012}

\begin{document}
\maketitle
\input{../su-contact}

\section*{Course Description}
Surveys the arts, literature, belief systems, and major events in the development of cultures around the globe from the European Renaissance to the contemporary period.

\section*{Instructional Materials}
\subsection*{Required Resources}
\begin{itemize*}
	\item Sayre, H. M. (2012). \emph{The Humanities: Culture, continuity and change}, Volume 2 (2nd ed.) (2011 Custom Edition). Upper Saddle River, NJ: Pearson Education.
	\item MyArtsLab access code
\end{itemize*}

\subsection*{Supplemental Resources}
\begin{itemize*}
	\item Harmon, D.E. (2002). \emph{Explorers of the South Pacific: A thousand years of exploration, from Polynesians to Captain Cook and beyond}. Broomall, PA: Mason Crest Publishers.
	\item McKenzie, L. (2000). \emph{Non-western Art: A brief guide}. Upper Saddle River, NJ: Prentice Hall.
	\item Tuchman, B.W. (1996). \emph{The Proud Tower: A portrait of the world before the war, 1890--1914}. New York, NY: Ballantine Books.
	\item Ward, G.C. \& Burns, K. (2002). \emph{Jazz: A history of America's music}. New York: Knopf. Doubleday Publishing Group.
\end{itemize*}

\section*{Course Learning Outcomes}
\begin{enumerate*}
	\item Explain how key social, cultural, and artistic developments contribute to historical changes.
	\item Explain the importance of situating a society's cultural and artistic expressions within a historical context.
	\item Examine the influences of intellectual, religious, political, and socio-economic forces on social, cultural, and artistic expressions.
	\item Identify and describe key artistic styles in the visual arts of world cultures from the Renaissance to the contemporary period.
	\item Identify and describe key literary works, styles, and writers from world cultures from the Renaissance to the contemporary period.
	\item Identify and describe key musical styles from world cultures from the Renaissance to the contemporary period.
	\item Identify major historical developments in world cultures from the Renaissance to the contemporary period.
	\item Explore the presence of cultural parallels between the world's cultures.
	\item Use technology and information resources to research issues in the study of world cultures.
	\item Write clearly and concisely about world cultures using proper writing mechanics.
\end{enumerate*}

\input{../schedule-frame}

\gradeChart{21}{1020}{
	QuQuizzes (total of 5)		& 400 \newline (80 points each)	& 39\% \\ \hline
	``Surprise Ending'' Essay	& 100 							& 10\% \\ \hline
	Project Paper				& 200 							& 20\% \\ \hline
	Cultural Event Report		& 100 							& 10\% \\ \hline
}

\input{../syllabus-policies}

\gradesChart{918--1020}{816--917}{714--815}{612--713}{612}

\input{essay}
\input{paper}
\input{report}
\input{../su-info}
\end{document}
