\pagebreak
\section*{Assignment 2: Report on Religious Field Research}
\emph{Due Week 10 and worth 120 points}

As a way of experiencing World Religions beyond your classroom, computer, and textbook, you are asked to attend a religious institution not affiliated with your own and report on your experience. This could be visiting a religious service or a religious education center. You should attend this place before the end of Week 10 and interview a member of that faith. Write a five to seven (5--7) page report (1250--1750 words) that describes your experience.

\textbf{Note: Submit your field research choice to the instructor for approval before the end of Week 5.}

Write a 5-7 page paper in which you:
\begin{enumerate*}
	\item Discuss any misconceptions you had about the religion you researched.
	\item Analyze how your prior understanding about this religion was altered (if at all) through your encounter.
	\item Discuss whether you believe misconceptions about other people's religion are common and explain why or why not.
	\item Recommend at least one (1) step that could be taken to minimize misconceptions people have about religions not their own.
\end{enumerate*}

Keep the points to be covered in your paper in mind during your religious field research to help guide your encounter. The purpose of your field research is to test your own assumptions about this religion.  

Pay attention to what is important to people inside the religion, what they do, what they profess, how they act, what they value, what they talk about, and what they tell you about their religion. The easiest way to understand what is important to someone else is let them tell you about their faith, their traditions, and their religious practices. The most important thing to do is to keep an open mind and listen. No matter which route you take for your field research, you will be looking for the same information.

Please keep in mind that if you choose to attend a religious service in person, you are a guest and should be as respectful as humanly possible. While you may be attending the service from the perspective of an objective (and hopefully inquisitive) observer, most of the other people will be attending the service as part of their religious practices. Please do the following before you go:
\begin{enumerate*}
	\item Call the place you wish to attend and ask if it is okay to attend as an observer. The locations which the instructor provides have already been contacted on your behalf.
	\item Ask if someone could (or should) act as a host when you attend.
	\item Ask if anyone would be willing to speak with you after the service to explain what happened and to answer a few questions about the basics of the religion.
\end{enumerate*}

The specific course learning outcomes associated with this assignment are:
\begin{itemize*}
	\item Describe the varieties of religious experience and practice in a wide range of cultures. 
	\item Recognize how daily life within various religions and current affairs are influenced by religion.
	\item Analyze the similarities and differences in the primary beliefs held by major religious traditions and the cultures in which these religions evolved.
	\item Develop written pieces that demonstrate an analysis of a topic relevant to the course.
	\item Use technology and information resources to research issues in religion.
	\item Write clearly and concisely about world religions using proper writing mechanics
\end{itemize*}

\rubricTwenty{
	Discuss any misconceptions you had about the religion you researched.
	& Did not discuss any misconceptions; omitted information and/or included irrelevant information.
	& Partially discussed some misconceptions; omitted some key information.
	& Sufficiently discussed any misconceptions.
	& Fully discuss any misconceptions. \\ \hline

	Analyze how your prior understanding about this religion was altered (if at all) through your encounter.
	& Did not analyze; omitted information and/or included irrelevant information.
	& Partially analyzed; omitted some key information.
	& Sufficiently analyzed prior understanding.
	& Fully analyzed prior understanding. \\ \hline

	Discuss whether you believe misconceptions about other people's religion are common and explain why or why not.
	& Did not discuss common misconceptions; omitted information and/or included irrelevant information.
	& Partially discussed common misconceptions; omitted some key information.
	& Sufficiently discussed common misconceptions.
	& Fully discussed common misconceptions. \\ \hline

	Recommend at least one (1) step that could be taken to minimize misconceptions people have about religions not their own.
	& Did not recommend at least one step; omitted information and/or included irrelevant information.
	& Partially recommended at least one step; omitted some key information.
	& Sufficiently recommended at least one step which could minimize misconceptions.
	& Fully recommended at least one step which could minimize misconceptions.
}
