\pagebreak
\section*{Assignment 1: Report on the Religious Life of Planet Earth}
\emph{Due Week 4 and worth 120 points}

Assume you are from another planet and have been sent to Earth to determine if it is a religious planet or not (something very important to your people). Your superiors are expecting a report back from you. Write a 2-3 page paper (at least 500 words) in which you:
\begin{enumerate*}
	\item Discuss the criteria you employ to determine if Earth people are religious: what does religion look like?
	\item Describe three (3) examples of behaviors or beliefs you observe that meet the criteria established above.
	\item Based on your observations, explain what the function of religion appears to be on Earth.
	\item If you find that religion can be better discussed in terms of something other than its function, explain how else religion could be understood.
\end{enumerate*}

The specific course learning outcomes associated with this assignment are:
\begin{itemize*}
	\item Analyze what is meant by ``religion.''
	\item Recognize how daily life within various religions and current affairs are influenced by religion.
	\item Describe the varieties of religious experience and practice in a wide range of cultures.
	\item Develop written pieces that demonstrate an analysis of a topic relevant to the course.
	\item Use technology and information resources to research issues in religion. 
	\item Write clearly and concisely about world religions using proper writing mechanics.
\end{itemize*}

\rubricTwenty{
	Discuss the criteria you will employ to determine if people on earth are religious.
	& Did not discuss the criteria employed; omitted information and/or included irrelevant information.
	& Partially discussed the criteria employed; omitted some key information.
	& Sufficiently discussed the criteria employed.
	& Fully discussed the criteria employed. \\ \hline

	Describe three (3) examples of behaviors or beliefs you observe that meet the criteria you established above.
	& Did not describe three examples observed; omitted information and/or included irrelevant information.
	& Partially described three examples observed; omitted some key information.
	& Sufficiently described three examples observed.
	& Fully described three examples observed. \\ \hline

	Explain what the function of religion appears to be on earth.
	& Did not explain the function; omitted information and/or included irrelevant information.
	& Partially explained the function of religion; omitted some key information.
	& Sufficiently explained the function of religion.
	& Fully explained the function of religion. \\ \hline

	Explain how else religion could be understood.
	& Did not explain; omitted information and/or included irrelevant information.
	& Partially explained; omitted some key information.
	& Sufficiently explained how else religion could be understood.
	& Fully explained.
}

