\documentclass{article}
\usepackage{syllabus}

\title{REL 212: World Religions}
\date{Spring 2012}

\begin{document}
\maketitle
\input{../su-contact}

\section*{Course Description}
This course offers a comparative approach to religious world views in relation to such questions as the origin of all things, the limits of knowledge, and the role and responsibilities of the individual and of society. It presents a conceptual, historical, and cultural survey of the major world religions. It examines religions such as Hinduism, Buddhism, Christianity, Islam, Judaism, Shinto, and New Age religious practices. This course analyzes the role of religion in helping to shape cultures and societies around the world.

\section*{Instructional Materials}
\subsection*{Required Resources}
\begin{itemize*}
	\item Fisher, Mary P. (2011). \emph{Living Religions} (8th ed.) (2011 Custom Edition). Upper Saddle River, NJ: Pearson Education.
	\item MyReligionLab access code
\end{itemize*}

\subsection*{Supplemental Resources}
\begin{itemize*}
	\item Fisher, Mary P. \& Bailey, L. W., eds. (2008). \emph{An Anthology of Living Religions} (2nd ed.).  Upper Saddle River, NJ: Pearson Education.
	\item Gale, R. (2006). \emph{On the Philosophy of Religion: Philosophical Topics}. Boston: Wadsworth/Cengage.
	\item Malloy, M. (2010). \emph{Experiencing the World's Religions: Traditions, Challenges, and Change} (5th ed.). New York, NY: McGraw-Hill.
	\item Noss, D. \& Blake, R. (2008). \emph{History of the World's Religions} (12th ed.). Upper Saddle River, NJ:  Pearson Education.  
\end{itemize*}

\section*{Course Learning Outcomes}
\begin{enumerate*}
	\item Analyze what is meant by religion.
	\item Analyze the similarities and differences in the primary beliefs held by major religious traditions and the cultures in which these religions evolved. 
	\item Describe the varieties of religious experience and practice in a wide range of cultures.
	\item Recognize how daily life within various religions and current affairs are influenced by religion.
	\item Develop written pieces that demonstrate an analysis of a topic relevant to the course.
	\item Use technology and information resources to research issues in religion.
	\item Write clearly and concisely about world religions using proper writing mechanics.
\end{enumerate*}

\input{../schedule-frame}
\gradeChart{30}{720}{
	QuQuizzes (total of 10)			& 260	& 36\% \\ \hline
	Religious Life of Planet Earth	& 120	& 17\% \\ \hline
	Religious Field Research		& 120	& 17\% \\ \hline
}
\input{../syllabus-policies}
\gradesChart{648--720}{576--647}{504--575}{432--503}{432}
\input{report}
\input{field}
\input{../su-info}
\end{document}
