%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%% Wrap-up
%% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\firstslide[14 March 2012]{World Cultures Today}

\section{Review}
\begin{frame}{Review}
	\LARGE{What have you learned in this course?}
\end{frame}


\begin{frame}{The Ecological Frame}
	\begin{itemize}
		\item<+->Everything changes: government, politics, art, music, religion, philosophy, etc.
		\item<+->There is a long history behind nearly everything we have today. Nothing arises out of nothing.
		\item<+->We have a bad tendency to ignore non-Western cultures (e.g. Africa, East Asia, South America)
		\item<+->Politics
			\only<4>{
			\begin{enumerate}
				\item ``Who controls the past controls the future: who controls the present controls the past.'' (George Orwell, \emph{Nineteen Eighty-Four}) The past is both unchangeable and completely alterable.There is almost always a liberation movement to fight perceived oppression.
				\item Oppression has always existed in some form or another: wars, slavery, disenfranchisement, social inequality.
				\item There is almost always a liberation movement to fight perceived oppression.
				\item One person's revolutionary or ``freedom fighter'' is another person's insurrectionist, insurgent, or terrorist.
			\end{enumerate}
			}
		\item<+->Art \& Music
			\only<5>{
			\begin{enumerate}
				\item Many distinct styles.
				\item Lines between two neighboring styles can be blurry.
				\item Later artists resurrect older styles.
			\end{enumerate}
			}
		\item<+->Literature
			\only<6>{
			\begin{enumerate}
				\item Authors regularly speak to a social context.
				\item Previous works influence later works.
			\end{enumerate}
			}
		\item<+->Philosophy \& Religion
			\only<7>{
			\begin{enumerate}
				\item Like literature, there is normally a social context.
				\item ``Conversations'' span centuries.
				\item There is rarely a consensus. If there is one, it doesn't last long.
				\item One person's theory is another person's garbage.
			\end{enumerate}
			}
		\item<+->Culture is always interpreted.
		\item<+->There is never only one culture.
	\end{itemize}
\end{frame}

\timeout

\quiz