\pagebreak
\section*{Assignment 1: Essay}
\emph{Due Week 4 and worth 100 points}

Choose one (1) of the topics below and develop a three to four (3--4) paragraph essay (at least 250 words) in which you:
\begin{enumerate*}
	\item Clearly state the ``mystery'' and provide a brief summary of at least two (2) theories which could explain the mystery. Because some theories may sound far-fetched, include the source or promoter of each theory – such as a scientist, a historian, a theologian, etc.
	\item Identify one (1) of the theories and provide at least two (2) convincing reasons why the theory you have chosen is the best one to explain the mystery.
	\item Use at least two (2) sources \emph{besides the textbook}.
\end{enumerate*}

\subsection*{Topic Choices}
\begin{enumerate*}
	\item There have been many theories regarding how the pyramids at Giza were constructed. They were constructed as burial monuments for pharaohs, but ``how'' these ancient people constructed monuments of such great size without modern machinery is a mystery which is still being debated.

	\item No one can say for certain what happened to the Mayan people, but theories abound and include varied possible alternatives to explain the abrupt and mysterious disappearance of the Mayan civilization.

	\item It is believed that Queen Hatshepsut dressed as a man to gain support of the Egyptians. After her death, her successor removed as many remnants of her rule as possible. Although a pharaoh, her mummified remains and tomb have never been conclusively found.

	\item Tutankhamen died young, at around 18 years of age. However, his cause of death has not been confirmed. Did he die of an injury, of illness, or was he murdered?

	\item Considered the ``Mummy's Curse,'' a series of unexplainable, unfortunate, or tragic events that happened to the people who were present at the opening of Tutankhamen's tomb.

	\item The monumental size and complexity of the Tomb of Shihuangdi is astounding. It is believed that the workers were forced to remain inside the tomb when it was walled shut so they would not reveal the secrets of its construction. What was the emperor's purpose for such an elaborate burial place?

	\item Other topic choice recommended and approved by the professor and supported by the grading rubric.
\end{enumerate*}

The specific course learning outcomes associated with this assignment are:
\begin{itemize*}
	\item Explain how key social, cultural, and artistic developments contribute to historical changes.
	\item Explain the importance of situating a society's cultural and artistic expressions within a historical context.
	\item Examine the influences of intellectual, religious, political, and socio-economic forces on social, cultural, and artistic expressions.
	\item Identify major historical developments in world cultures during the eras of antiquity to the Renaissance.
	\item Use technology and information resources to research issues in the study of world cultures.
	\item Write clearly and concisely about world cultures using proper writing mechanics.
\end{itemize*}

\rubricQuarter{
	Clearly state the ``mystery'' and provide a brief summary of at least two (2) theories (including source/promoter) which could explain the mystery.
	& Neither stated the mystery nor provided a summary of at least two theories; omitted information and/or included irrelevant information.
	& Partially completed at least one piece; omitted some key information.
	& Sufficiently completed the requirements.
	& Fully completed the requirements. \\ \hline

	Identify one (1) of the theories and provide at least two (2) convincing reasons why the theory you have chosen is the best one to explain the mystery.
	& Did not complete; omitted information and/or included irrelevant information.
	& Partially provided at least one reason; omitted some key information.
	& Sufficiently provided at least two convincing reasons.
	& Fully provided at least two convincing reasons.
}
