\documentclass{article}
\usepackage{syllabus}

\title{HUM 111: World Cultures 1}
\date{Spring 2012}

\begin{document}
\maketitle
\input{../su-contact}

\section*{Course Description}
This course surveys the arts, literature, belief systems, and major events in the development of cultures around the globe from ancient times to the period of the European Renaissance.

\section*{Instructional Materials}
\subsection*{Required Resources}
\begin{itemize*}
	\item Sayre, H. M. (2012). \emph{The Humanities: Culture, continuity and change}, Volume 1 (2nd ed.) (2011 Custom Edition). Upper Saddle River, NJ: Pearson Education.
	\item MyArtsLab access code
\end{itemize*}

\subsection*{Supplemental Resources}
\begin{itemize*}
	\item Barnstone, T., Ed. (2003). \emph{Literatures of Asia}. Upper Saddle River, NJ: Prentice Hall.
	\item Bottero, J. (1992). \emph{Mesopotamia: Writing, reasoning, and the gods}. Chicago: Univ of Chicago.
	\item Cohen, J. (2008). \emph{A History of Western Literature: From medieval epic to modern poetry}. Piscataway, NJ: Aldine Transaction.
	\item McKenzie, L. (2000). \emph{Non-western Art: A brief guide} (2nd ed.). Upper Saddle River, NJ: Prentice Hall.
	\item Plazy, G. (2001). \emph{The History of Art in Pictures: Western art from prehistory to the present}. New York, NY: Sterling Publishing.
\end{itemize*}

\section*{Course Learning Outcomes}
\begin{enumerate*}
	\item Explain how key social, cultural, and artistic developments contribute to historical changes.
	\item Explain the importance of situating a society's cultural and artistic expressions within a historical context.
	\item Examine the influences of intellectual, religious, political, and socio-economic forces on social, cultural, and artistic expressions.
	\item Identify and describe key artistic styles in the visual arts of world cultures from antiquity to the Renaissance.
	\item Identify and describe key literary works, styles, and writers from antiquity to the Renaissance.
	\item Identify and describe key musical styles from world cultures from antiquity to the Renaissance.
	\item Identify major historical developments in world cultures from antiquity to the Renaissance.
	\item Explore the presence of cultural parallels between the world's cultures.
	\item Use technology and information resources to research issues in the study of world cultures.
	\item Write clearly and concisely about world cultures using proper writing mechanics.
\end{enumerate*}

\input{../schedule-frame}

\gradeChart{21}{1020}{
	QuQuizzes (total of 5)		& 400 \newline (80 points each)	& 39\% \\ \hline
	``Ancient Mystery'' Essay	& 100 							& 10\% \\ \hline
	Project Paper				& 200 							& 20\% \\ \hline
	Cultural Event Report		& 100 							& 10\% \\ \hline
}

\input{../syllabus-policies}

\gradesChart{918--1020}{816--917}{714--815}{612--713}{612}

\input{essay}
\input{paper}
\input{report}
\input{../su-info}
\end{document}
